A studyforrest extension, an annotation of spoken language in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-06-28 paper/main.tex
little changes on data legend

\subsection*{Data Legend}
% TextGrid vs. TSV
The annotation is available in two different versions, both providing the same
information: a) as a (text-based) Praat TextGrid file and b) as a text-based,
tab-separated value (TSV) formatted table.
% preview of following subsubsections
The following descriptions refer to the ten columns of the TSV file, namely
\texttt{onset}, \texttt{duration}, \texttt{person}, \texttt{text} (of sentence,
word or phoneme), \texttt{pos}, \texttt{tag}, \texttt{dep}, \texttt{lemma},
\texttt{stop}, \texttt{vector}.

@@

\subsubsection*{Duration (\texttt{duration})} The duration of the sentences,
word or phoneme provided the format seconds.milliseconds.

@@

\subsubsection*{Simple part-of-speech tag (\texttt{pos})} A simple
part-of-speech tagging (grammatical tagging; word-category disambiguation) of
words.
% annotation scheme
The tag labels of this simple part-of-speech tagging follow the Universal
Dependencies v2 POS tag set
(\href{https://universaldependencies.org}{universaldependencies.org}).
% reference to table
See Table \ref{tab:pos} for a description of the labels and the respective
counts of all 15 labels. Nouns that spaCy mistook for proper nouns or vice versa
were corrected via script.
% s. list at the beginning of script code/add_part-of-speech-tagging2textgrid.py
% flags for sentences and phonemes in POS column
Additionally in cells of this column, sentences are tagged as \texttt{SENTENCE},
and phonemes are tagged as \texttt{PHONEME} to facilitate sorting, and filtering
in potential further processing steps.

@@

\subsubsection*{Syntactic dependency (\texttt{dep})} Information about a word's
syntactic dependencies with other words within the same sentence.
% annotation scheme
Information follows the TIGER Treebank annotation scheme \citep{brants2004tiger}
and is given in the format: ``arc label;word's head;word's child1, word's
child2, ...'', where the ``arc label'' (see Table \ref{tab:dep}) describes the
type of syntactic relation that connects a "child" (the single word) to its
``head''.

@@

\subsection*{Dataset content}
% \href{https://bids.neuroimaging.io/}{bids.neuroimaging.io} TextGrid format
The annotation comes in two different versions. First, as a text-based TextGrid
file (\texttt{annotation/fg\_rscut\_ad\_ger\_speech\_tagged.TextGrid}) to be
conveniently edited with the software Praat \citep{boersma2019praat}.
% TSV format
Second, as a text-based, tab-separated-value (TSV) formatted table
(\texttt{annotation/fg\_rscut\_ad\_ger\_speech\_tagged.tsv}) in accordance with
the brain imaging data structure (\href{https://bids.neuroimaging.io/}{BIDS}
\citep{gorgolewski2016bids}).
% source code for descriptive statistics
The source code for all descriptive statistics included in this paper is
available in \texttt{code/descriptive-statistics.py} (Python script).

>>>>

\subsection*{Data Legend}
% TextGrid vs. TSV
The annotation is available in two different versions, both providing the same
information: a) as a text-based Praat TextGrid file and b) as a text-based,
tab-separated value (TSV) formatted table.
% preview of following subsubsections
The following descriptions refer to the ten columns of the TSV file, namely
\texttt{onset}, \texttt{duration}, \texttt{person}, \texttt{text}, \texttt{pos}, \texttt{tag}, \texttt{dep}, \texttt{lemma},
\texttt{stop}, \texttt{vector}.

@@

\subsubsection*{Duration (\texttt{duration})} The duration of the sentence,
word or phoneme provided the format seconds.milliseconds.

@@

\subsubsection*{Simple part-of-speech tag (\texttt{pos})} A simple
part-of-speech tagging (grammatical tagging; word-category disambiguation) of
words.
% annotation scheme
The tag labels of this simple part-of-speech tagging follow the Universal
Dependencies v2 POS tag set
(\href{https://universaldependencies.org}{universaldependencies.org}).
% reference to table
See Table \ref{tab:pos} for a description of the labels and the respective
counts of all 15 labels. Nouns that spaCy mistook for proper nouns or vice versa
were corrected via script.
% s. list at the beginning of script code/add_part-of-speech-tagging2textgrid.py
% flags for sentences and phonemes in POS column
Additionally in cells of this column, sentences are tagged as \texttt{SENTENCE},
and phonemes are tagged as \texttt{PHONEME} to facilitate filtering in potential
further processing steps.

@@

\subsubsection*{Syntactic dependency (\texttt{dep})} Information about a word's
syntactic dependencies with other words within the same sentence.
% annotation scheme
Information follows the TIGER Treebank annotation scheme \citep{brants2004tiger}
and is given in the format: ``arc label;word's head;word's child1, word's
child2, ...'', where the ``arc label'' (see Table \ref{tab:dep}) describes the
type of syntactic relation that connects a "child" (the word) to its
``head''.

@@

\subsection*{Dataset content}
% \href{https://bids.neuroimaging.io/}{bids.neuroimaging.io} TextGrid format
The annotation comes in two different versions. First, as a text-based TextGrid
file (\texttt{annotation/fg\_rscut\_ad\_ger\_speech\_tagged.TextGrid}) to be
conveniently edited using the software Praat \citep{boersma2019praat}.
% TSV format
Second, as a text-based, tab-separated-value (TSV) formatted table
(\texttt{annotation/fg\_rscut\_ad\_ger\_speech\_tagged.tsv}) in accordance with
the brain imaging data structure (\href{https://bids.neuroimaging.io/}{BIDS})
\citep{gorgolewski2016bids}.
% source code for descriptive statistics
The source code for all descriptive statistics included in this paper is
available in \texttt{code/descriptive-statistics.py} (Python script).
